Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-31 paper.tex
update

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated} on semantic web service composition focused mainly on functional requirements while neglecting non-functional requirements. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is to considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and pairing a mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, the author surveyed three approaches to the similarity measures using taxonomies: one is based on nodes, in which similarity is determined by the information content of the nodes; one is entirely based on edge, where concept distance in a hierarchy structure is evaluated,  and the hybrid approach that combines the previous two methods. A new similarity measure based on edge counting in a taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formular \ref{equation1}, when $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, the auther utilise one possible measure for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of this approach for semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in the knowledge representation system. for example, we may need service profiles definition described in OWL-S, and their related class, class axioms and properties defined in OWL2. This makes it nearly impossible to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered by the author, rather than a fully automated method. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2015graphevol,da2016particle} is typical EC techniques to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition.

>>>>

\subsection{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused mainly on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both addressed both of them at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} are the papers could be found so far. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} reasoning between input and output parameter concepts of web services to ensure a semantic matchmaking. It is considered be a process consisting of seeking similarity of parameters (i.e., input and output) of web services and mapping between two knowledge representations encoded utilising the ontology \cite{lecue2006formal}.

In \cite{shet2012new}, three approaches are surveyed three approaches regarding the similarity measures using taxonomies: $(1)$ The first one is based on nodes, in which similarity is determined by the information content of the nodes; $(2)$ the second is entirely based on edge, where concept distance in a hierarchy structure is evaluated, and $(3)$ the hybrid approach features a combination of $(1)$ and $(2)$. A new similarity measure based on edge counting in taxonomy is introduced in \cite{shet2012new}, which extends similarity measure defined by Wu and Palmer \cite{wu1994verbs}. Neighbourhood concepts are considered in their model in Formula \ref{equation1}, when $\lambda$ = 1 (default value as 0).

@@

In \cite{lecue2009optimizing}, the quality of matchmaking problem is transferred to measure the quality of semantic links $sl_{i,j} \stackrel{.}{=} \langle s_{i}, Sim_{T}(Out\_s_i,In\_s_j),s_{j}  \rangle$, one possible measure is applied for the degree of similarity using Common Description rate of a semantic link in Formula \ref{equation2}, where Extra Description $In_{s_{x}} \setminus Out_{s_{y}}$ and Least common subsume $lcs(Out_{s_i},In_{s_j})$ are required to be pre-calculated. They also chained the web service with five well-known matching types: Exact, Plug-in, Subsume, Intersection, and Disjoint. Therefore, the quality of the semantic link is estimated as quality criteria $q_{m}$ associated with their corresponding quality of vector $q_{cd}$ defined as Formula \ref{equation3}.

@@

However, the weakness of semantic link quality is that calculating Extra description and Least common subsume requires well and completely defined ontology in class, class axioms and properties in OWL2. This makes it difficult to measure semantic matchmaking quality in most semantic web services applications. Additionally, a semi-automated service composition approach is considered, rather than a fully automated method. And only cost and time are considered in the optimised problems. Therefore, we introduce a more applicable comprehensive quality model in a fully automated approach.

In \cite{fanjiang2014semantic}, it covers the concerns in both functional and non-functional requirements in design time of semantic-based automatic service composition, where a GA-based approach with four unusual independent fitness functions are designed to solve the problems with these concerns. In details, a sequence of fitness functions are used in the binary selection of chromosome, rather than a single objective consisting of both functional and non-functional quality. Apart from that, match types are ignored in their quality evaluation of semantic matching.

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problem. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique to solve automated web service composition. This GP-based approach utilises tree representations, on which service and constructs as represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. To simplify the checking of constraints for solutions, an indirect PSO-based approach was introduced in \cite{da2016particle}, firstly, the best location is searched using PSO considering optimising QoS for building up service queue, then web services in this service queue are selected to build up a graph representation of the solution. However, this solution does not distinguish different matching types and parameter similarity, which could lead to the outputs returned by the selected service that we think may be too general. In fact, customers' perspectives, application domains and ontology granularity all could have significant impacted on the outputs requested by users. In some scenarios, the output returns too broad consequences that have no meaning for the customers, even though those web services selected leads to a very good overall QoS. Therefore, we fill the gap by considering different matching types and the similarity when evaluate an overall quality of web service composition and utilising a weighed graph representation as the particles in the PSO.
